Vegetation regrowth/encroachment (gjengroing)

### 2023-08-31 functional_plant_indicators_wetland.Rmd
finalizing the fpi markdown for wetlands

- Northern Norway: 416
- Central Norway:  362
- Eastern Norway:  295
- Western Norway:  151
- Southern Norway: 127

@@

### unscaled values vs. reference
We can also compare the unscaled values to the reference distribution in order to identify ecosystem types and functional plant indicators showing a deviation from the expectation. Since pH and nitrogen show some deviation of the lower pH indicator we exemplify this with these indicators for unscaled values.

@@

```
THe figure shows that deviations mainly occur in V2-C1, which represents limestone-poor swamp forests. According to the functional signature from the plant community composition many of the occurrences of this ecosystem type are too acidic and may have too low availability of nitrogen.

>>>>

- Northern Norway: 416
- Central Norway:  361
- Eastern Norway:  294
- Western Norway:  150
- Southern Norway: 126

@@

### unscaled values vs. reference
We can also compare the unscaled values to the reference distribution in order to identify ecosystem types and functional plant indicators showing a deviation from the expectation. Since pH and nitrogen show some deviation in the lower indicator we exemplify this with these two indicators for unscaled values.

@@

```
Deviations from the reference occur mainly in V2-C1, which represents limestone-poor swamp forests. According to the functional signature from the plant community composition many of the occurrences of this ecosystem type are too acidic and may have too low availability of nitrogen.
